A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-12 future.tex
updating with maarten's comments

There are a variety of avenues for future improvement of both the \code{aneris}
code base and underlying methodology. As with any software project, additional
users will provide use cases for more robust handling of input/output concerns
and corner cases. Further configuration parameters may also be added in the
future in order to provide overrides for all gas species in a given sector or
region. Perhaps the most fruitful investigation will involve further refinement
of the default decision tree introduced in Section \ref{sec:meths}. A key aspect
missing from the decision tree is input from models regarding whether missing
sources are the likely cause of a harmonization year discrepancy (suggesting the
% * <maarten.vandenberg@pbl.nl> 2017-07-03T23:15:16.273Z:
% 
% > missing
% > sources
% it might also be a difference in activity levels, which might be something different than missing sources.
% 
% ^.
use of an offset method) or instead a significant difference in emissions
% * <maarten.vandenberg@pbl.nl> 2017-07-03T23:16:40.654Z:
% 
% > emissions
% > factors (suggesting the use of a ratio method)
% knowledge of these factors might even lead to combinations of harmonization methods for a single sector/gas/region combination as they are aggregate categories.
% 
% ^.
factors (suggesting the use of a ratio method) \cite{rogelj_discrepancies_2011}.

>>>>

There are a variety of avenues for future improvement of both the \code{aneris}
code base and underlying methodology. As with any software project, additional
users will provide use cases for more robust handling of input/output concerns
and corner cases. Further configuration parameters may also be added in the
future in order to provide overrides for all gas species in a given sector or
region. Perhaps the most fruitful investigation will involve further refinement
of the default decision tree introduced in Section \ref{sec:meths}. A key aspect
missing from the decision tree is input from models regarding whether missing
sources or activity levels are the likely cause of a harmonization year
discrepancy (suggesting the
% * <maarten.vandenberg@pbl.nl> 2017-07-03T23:15:16.273Z:
% 
% > missing
% > sources
% it might also be a difference in activity levels, which might be something different than missing sources.
% 
% ^.
use of an offset method) or instead a significant difference in emissions
% * <maarten.vandenberg@pbl.nl> 2017-07-03T23:16:40.654Z:
% 
% > emissions
% > factors (suggesting the use of a ratio method)
% knowledge of these factors might even lead to combinations of harmonization methods for a single sector/gas/region combination as they are aggregate categories.
% 
% ^.
factors (suggesting the use of a ratio method) \cite{rogelj_discrepancies_2011}.

### 2017-07-12 results.tex
updating with maarten's comments

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the South Asia (SAS) MESSAGE-GLOBIOM region, which
comprises most of the Asian subcontinent. The default method chosen
(\code{constant_ratio}) maintains model trends for the region; however, overall
model results are distorted. By applying a \code{constant_offset} override, the
regional trend and magnitude is maintained. With the new harmonization method
for the SAS region, the global trajectory for industrial CO also maintains the
trends seen in the unharmonized trajectory.
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:53:14.757Z:
% 
% > the global trajectory for industrial CO also corresponds
% > more closely with the unharmonized trajectory.
% The global trajectory suffers under the constant_ratio method from changing relative importance of underlying regions, resulting in a trend change, this effect is also prevented by using a constant_offset method.
% 
% ^.

>>>>

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the South Asia (SAS) MESSAGE-GLOBIOM region, which
comprises most of the Asian subcontinent. The default method chosen
(\code{constant_ratio}) maintains model trends for the region; however, overall
model results are distorted. By applying a \code{constant_offset} override, the
regional trend and magnitude is maintained. With the new harmonization method
for the SAS region, the global trajectory for industrial CO also is
representative the trends seen in the unharmonized trajectory and the relative
importance of the underlying regional trajectoreis is maintained.
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:53:14.757Z:
% 
% > the global trajectory for industrial CO also corresponds
% > more closely with the unharmonized trajectory.
% The global trajectory suffers under the constant_ratio method from changing relative importance of underlying regions, resulting in a trend change, this effect is also prevented by using a constant_offset method.
% 
% ^.
